---
title: "Measuring a Movie’s Success Beyond the Dollar: <br> Are The Highest Grossing Movies of All Times Actually…Good?"
author: "Emma Malcolm, Na Nguyen"
date: "2023-04-11"
output:
  bookdown::html_document2:
    split_by: NONE
    toc: yes
    toc_depth: 3
    toc_float:
      toc_collapsed: true
    number_sections: false
    code_download: true
editor_options: 
  markdown: 
    wrap: 72
---

<!--- Begin styling code. --->

```{=html}
<style type="text/css">
/* Whole document: */
body{
  font-family: "Palatino Linotype", "Book Antiqua", Palatino, serif;
  font-size: 12pt;
}
h1.title {
  font-size: 38px;
  text-align: center;
}
h4.author {
  font-size: 18px;
  text-align: center;
}
h4.date {
  font-size: 18px;
  text-align: center;
}
</style>
```
<!--- End styling code. --->

```{r,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE, tidy = TRUE)
```

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(splitstackshape)
library(dbplyr)
library(stringr)
library(readr)
library(ggplot2)
library(ggthemes)
library(fivethirtyeight)
library(highcharter)
library(scales)
library(rvest)
library(scales)
library(plotly)
library(gapminder)
library(forcats)
library(magrittr)


#Loading raw data
box_office <-read_csv("../data/All Time Worldwide Box Office.csv")
movies_info <- read_csv("../data/movies.csv")
oscars_award <- read_csv("../data/the_oscar_award.csv")
bechdel <- data.frame(bechdel)
bechdelset <- read_csv("../data/bechdelset.csv")
Bechdelmoney <- read_csv("../data/Bechdelmoney.csv")
biopics <- data.frame(biopics)
RatingGross <- read_csv("../data/RatingGross_edit2.csv")

```

```{r,echo=FALSE, message=FALSE}
#Data cleaning for figure 1
#average grossing for each top 20 scored

top_score <- movies_info %>% 
  select(name, score, year, gross) %>% 
  arrange(desc(score))

#average grossing for each top 20 scored

low_score <- movies_info %>% 
  select(name, score, year, gross) %>% 
  arrange(score)


oscarwins <-  movies_info %>% 
  filter(name %in% c("The Lord of the Rings: The Return of the King", "Titanic", "Ben-Hur", "West Side Story", "The English Patient", "The Last Emperor", "Gigi", "Slumdog Millionaire", "Amadeus", "Gandhi")) %>% 
 summarize(sum=sum(gross))


doubledata <- movies_info %>%
  left_join(RatingGross,
    by = c("name", "year" = "Year"))


topgross <- doubledata %>% 
  filter(doubledata$Rank < 25) %>%  
  arrange(desc(`WorldwideBox Office`)) %>% 
  select(name, score.x, Rank, `WorldwideBox Office`)

duplicate_rows <- topgross[duplicated(topgross), ]
topgross <- unique(topgross)


toprate <- doubledata %>% 
  select(name, score.x, Rank, `WorldwideBox Office`) %>% 
  arrange(desc(score.x)) 

     
topgross_20 <- head(topgross, n = 20) %>% 
  select(name, score.x, `WorldwideBox Office`)
topscore_20 <- head(toprate, n = 20) %>% 
  select(name, score.x, `WorldwideBox Office`)



```

```{r,echo=FALSE, message=FALSE}
#Data cleaning for figure 2
# Changing Box Office variables into numerical values
box_office <-box_office %>% 
 mutate(`WorldwideBox Office`=as.numeric(str_replace_all(`WorldwideBox Office`,"[$,]",""))) %>% 
  mutate(`DomesticBox Office`=as.numeric(str_replace_all(`DomesticBox Office`,"[$,]",""))) %>%
  mutate(`InternationalBox Office`=as.numeric(str_replace_all(`InternationalBox Office`,"[$,]","")))

#Getting the Top 20 Box Office
box_office_top20 <- box_office %>%  
  arrange(Rank) %>% 
  head(20) %>% 
  mutate(Movie=ifelse(Movie=="Harry Potter and the Deathly Hallows:…", "Harry Potter and the Deathly Hallows: Part 2",Movie))


#Creating Oscar category data frame
oscars_category <- tibble(
levels(factor(oscars_award$category)))
  

oscars_category <- oscars_category %>% 
  rename("category"="levels(factor(oscars_award$category))") 
  

oscars_category <- oscars_category %>% 
  mutate(broad_category=word(category,1)) %>% 
  mutate(broad_category=
           case_when(broad_category =="ART" ~"ART DIRECTION",
                     broad_category == "BEST" ~ "BEST PICTURE",
                     broad_category == "FILM" ~ "FILM EDITING",
                     broad_category == "ACTOR" | broad_category=="ACTRESS" ~ "ACTING",
                    TRUE ~ broad_category)
            ) 

#Top 20 Box Office Movies and awards dataset by joining dataframes
box_office_top20_awards <- box_office_top20 %>% 
  inner_join(oscars_award,by=c("Movie"="film")) %>% 
  filter(Year == year_film) %>% 
  inner_join(oscars_category)  

box_office_top20_awards <- box_office_top20_awards %>% group_by(Movie,year_film) %>% 
  summarize(total=n()) %>%  inner_join(oscars_award,by=c("Movie"="film")) %>% 
  filter(year_film.x == year_film.y) %>% 
  inner_join(oscars_category)  %>% 
  select(Movie, year_film.x,total,year_ceremony,name,winner,broad_category)
```

```{r,echo=FALSE, message=FALSE}
#Data cleaning for figure 3
#Changing movie names so they match across movies_info and box_office_top20

movies_info <- movies_info %>%  mutate(name=case_when(
  name=="Star Wars: Episode VII - The Force Awakens" ~ "Star Wars Ep. VII: The Force Awakens",
  name =="Star Wars: Episode VIII - The Last Jedi" ~ "Star Wars Ep. VIII: The Last Jedi",
TRUE~name)) %>% 
  mutate(company=case_when(
    company=="Walt Disney Animation Studios" | company=="Walt Disney Pictures" ~"Walt Disney",
TRUE~company))

#Joinining movies_info and box_office_top20

box_office_top20_info<- box_office_top20 %>%
  inner_join(movies_info,by=c("Movie"="name","Year"="year"))

#Making top20 main character's race data frame
top20_race <- data.frame(star=box_office_top20_info$star,Race=c("White","White","White","White","White","White","Black","White","White","White","White","Black","White","White","White","White","White","White","White","White"))

#Joining box_office_top20_info with top20_race dataframe
box_office_top20_info <- box_office_top20_info %>% data.frame(top20_race) %>% select(!star.1)

```

```{r,echo=FALSE, message=FALSE}
#Data cleaning for figure 4

bechdelset <- bechdelset %>% 
  mutate(set_factor = factor(set)) 

bechdelsetav <- bechdelset %>% 
  group_by(set_factor, clean_test) %>% 
  summarize(count = n ())

bechdelsetav <- bechdelsetav %>% 
  mutate(percent = count/ 20 * 100)

bechdelav <- bechdel %>% 
  group_by(clean_test) %>%  
  summarize (count = n ())

bechdelav <- bechdelav %>%  
    mutate(percent = round(count/ 1794 * 100)) %>% 
    mutate(set_factor = "Average Bechdel Scores")

jointav <- rbind(bechdelsetav, bechdelav) 


jointav$clean_test <- factor(jointav$clean_test, levels = c("nowomen", "notalk", "men", "dubious", "ok"))

```

```{r,echo=FALSE, message=FALSE,fig.alt="A scatter plot showing the relationship between the IMDb score and worldwide box office gross for movies with different Bechdel test scores. Each point represents a movie and is colored based on its Bechdel test score. The legend shows the five Bechdel test scores: no women, no talk, men, dubious, and ok. The x-axis represents the IMDb score, and the y-axis represents the worldwide box office gross in millions/ billions of dollars. The tooltip displays the movie name, IMDb score, and worldwide grossing for each point."}
#Figure 1
colors <- c("#AC2528", "#E4792C", "#764484", "#346491", "#448746")

fig1<-plot_ly(bechdelset, x = ~score.x, y = ~`WorldwideBox Office`, color = ~clean_test, colors = colors, type = 'scatter', mode = 'markers',
  hoverinfo = 'text',
  text = ~paste('</br>', name, 
                '</br>', "IMDB Score:", score.x, 
                '</br>', "Worldwide Grossing:", comma(`WorldwideBox Office`))) %>% 
  layout(title = 'IMDB Score vs. Amount of Money Grossed', 
            xaxis = list(title = 'IMDB Score'), 
            yaxis = list(title = 'Worldwide Box Office'), 
           legend = list(title = list(text = "Bechdel Test Score"),
                       titles = list(topgross_20 = "Top 20 Grossing", topscore_20 = "Top 20 Scored")))




```

```{r,fig.alt="This bar graph shows the total number of oscar awards nominations of the top 20 movies with the highest Worldwide Box Office by Category and Wins",echo=FALSE, message=FALSE,warning=FALSE}
#Figure 2

fig2<-box_office_top20_awards %>% 
  ggplot(aes(x = fct_reorder(Movie, total,.fun=sum),alpha=winner,fill=fct_reorder(broad_category,winner))) + 
  geom_bar()+
  theme_classic() +
  theme(legend.position = "right")+
  scale_fill_viridis_d()+
  coord_flip()+
  labs(y="Total Nominations",x="Movie",title="Top 20 Movies with Highest Worldwide Box Office vs Oscars Awards",subtitle = "By Category and Wins",fill="Category",alpha="Winner")+
  theme(plot.title = element_text(face="bold",size=16),plot.subtitle = element_text(size=14),axis.title.x = element_text(size=14),axis.text.x = element_text(size=12),axis.title.y = element_text(size=14),axis.text.y = element_text(size=12))


```

```{r,echo=FALSE, message=FALSE,fig.alt="This scatter plot displays the top 20 highest grossing movies of all time by their profit and the main character's race. It shows that out of 20 movies, 2 has a non-white main character."}
#Figure 3
fig3<-box_office_top20_info %>% 
  mutate(Profit=gross-budget) %>%
  ggplot(aes(x=budget,y=gross,color=Race,size=Profit)) +
  geom_point()+
  theme_minimal()+
  scale_x_continuous(labels = label_comma())+
  scale_y_continuous(labels = label_comma())+
  scale_size_continuous(labels = label_comma())+
  scale_color_viridis_d(option="E")+
  labs(y="Total Gross",x="Budget",title="Top 20 Movies with Highest Worldwide Box Office",subtitle = "By Profit and Race of Main Character")+
  theme(plot.title = element_text(face="bold",size=12),plot.subtitle = element_text(size=10),axis.text.x = element_text(size=8))+
  annotate("text",x=200000000,y=1430000000,label="Black Panther",size=3,color="red3")+
   annotate("text",x=260000000,y=1750000000,label="The Lion King (2019)",size=3,color="red3")

  
```

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.alt="A stacked column chart showing the percentage distribution of movies that pass the Bechdel test by different movie sets. The x-axis represents the movie sets, and the y-axis represents the percentage of movies that pass the Bechdel test. The chart is divided into five categories based on the Bechdel test score: no women, no talk, men, dubious, and ok. The tooltip shows the percentage of movies for each category and movie set."}
#Figure 4


fig4<-hchart(jointav, "column", hcaes(x = set_factor, y = count, group = clean_test), stacking = "percent") %>% 
  hc_title(text = "Bechdel Test Scores") %>% 
  hc_colors(colors) %>% 
  hc_tooltip(pointFormat = "{series.name}: {point.percentage:.1f}%") %>% 
  hc_yAxis(title = "Percentage", labels = list(format = '{value}%')) %>%
  hc_xAxis(title = NULL) %>% 
  hc_colors(colors) %>% 
  hc_legend(enabled = TRUE)
```

# The current anatomy of a good movie: Can we do better?

Ever since the "Golden Age" of cinema in the 1930s that marked silent
film a thing of the past, the film industry has witnessed unparalleled
success and growth. From the first technicolor movies like The Wizard of
Oz and Gone With The Wind to the computationally animated The Matrix,
Jurassic Park, and the first fully computer-animated film, Toy Story,
the industry of motion pictures has contributed greatly not only to
technology but also the global economy. Especially in the current
challenging economy and there has been a sharp decline in theater
audience---[shrinking by half in the last 4
years]<https://en.wikipedia.org/wiki/IMDb>), film distributors are
hesitant to take on a movie unless they can see its success first hand.
Therefore, box-office, or the entire earnings generated through movie
ticket sales, has been recognized as one of the primary indicators to
compare film success. Many rely on it to decide whether to both produce
and watch a film. However, are high grossing movies actually... good? If
so, what else can we use to measure them?

One of the popular other indicators used worldwide to assess a movie is
IMDb rating (or International Movie Database). IMDb rating allows [83
million](https://en.wikipedia.org) of its registered users to cast a
vote (from 1 to 10) on every released title in the database. These votes
are then aggregated and summarized as a single IMDb rating visible on
IMDb.com. Accessible to anyone, anywhere, these ratings are a simplified
way to see what people all over the world think about movies and have
been an often-used indicator for a film's popularity/quality. This led
us to wonder: *How do the most profitable movies rank on the IMDb
website?*

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.alt="A scatter plot showing the relationship between the IMDb score and worldwide box office gross for movies with different Bechdel test scores. Each point represents a movie and is colored based on its Bechdel test score. The legend shows the five Bechdel test scores: no women, no talk, men, dubious, and ok. The x-axis represents the IMDb score, and the y-axis represents the worldwide box office gross in millions/ billions of dollars. The tooltip displays the movie name, IMDb score, and worldwide grossing for each point."}
fig1
```

From our visualization above, the top 20 grossing films have a range of
scores from 6.2 to 8.4 stars. Conversely, the top 20 scored movies on
IMDb globally grossed between 28,419,159 and 1,120,210,896 U.S. Dollars.
When comparing the IMDbscore and amount of money grossed, we can observe
that there isn't much of a relationship between the rating of a film (or
how "objectively good" a movie is) and the amount of money it makes.

On the other hand, to investigate opinions of films from professionals
and trusted members of the film industry, we can turn to the Academy
Awards.

```{r,fig.width=10,echo=FALSE,message=FALSE,warning=FALSE,fig.alt="This scatter plot displays the top 20 highest grossing movies of all time by their profit and the main character's race. It shows that out of 20 movies, 2 has a non-white main character."}
fig2
```

It seems like a movie's revenue is not a strong indicator for its
accolades. Among the top 20 movies with the highest worldwide box office
and their Oscars awards, only 11 movies had any nominations at all.
Furthermore, this list gets even more narrowed down as we look into
wins/loses. Titanic, Avatar, Black Panther, and Frozen are the only
movies in the top 20 highest worldwide grossing movies to have had at
least one nomination and won, with Titanic as the most prolific with 11
out of 14 categories (after grouping some of them together).

The Oscars, however, are not an objective means of awardship. In 2015,
the academy "awarded all 20 acting nominations to white actors for the
first of two consecutive years, inspiring April Reign to create the
hashtag #OscarsSoWhite" [(Ugwu,
2020)](https://www.nytimes.com/2020/02/06/movies/oscarssowhite-history.html).
Leaving the determination of film success to the Academy seems to yield
a celebration of white creators and artists, excluding a whole world of
diverse cinema.

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.alt="This scatter plot displays the top 20 highest grossing movies of all time by their profit and the main character's race. It shows that out of 20 movies, 2 has a non-white main character."}
fig3
```

As of 2020, [almost half of the U.S. population (42.2%) are people of
color](https://en.wikipedia.org/wiki/Race_and_ethnicity_in_the_United_States#:~:text=As%20of%202020%2C%20White%20Americans,minority%2C%20making%20up%2012.1%25).
Yet, Hollywood fails to consider them when making movies. In the top 20
highest grossing movies of all time, only 2 movies featured a non-white
main character---both of which were Black males. None of these movies
are in the top 5 of this list in terms of profit and grossing while
other underrepresented demographics (Latines, East/South/Southeast
Asians, Native Americans, Afro Latinos, etc.) are left completely off
the screen.

Furthermore, in the history of the Oscars only three women have won the
coveted best director title. This reflects a gendered measure of success
within the film industry, where most of the praise goes to films about
and created by cis men. To measure the representation of women in films,
we can turn to the [Bechdel test](https://bechdeltest.com/) which was
popularized by Alison Bechdel. The test names three simple criteria: (1)
it has to have at least two women in it, who (2) who talk to each other,
about (3) something besides a man. Although this test seems easy enough,
only 25% of the top scored films and 50% of the top grossing films
passed. Interestingly enough, when comparing the two datasets to an
average Bechdel test score breakdown, we can see that the highest
grossing films all have women and an above average score of "ok" and
"dubious". However, the highest scored films have less than average "ok"
and dubious" scores.

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.alt="A stacked column chart showing the percentage distribution of movies that pass the Bechdel test by different movie sets. The x-axis represents the movie sets, and the y-axis represents the percentage of movies that pass the Bechdel test. The chart is divided into five categories based on the Bechdel test score: no women, no talk, men, dubious, and ok. The tooltip shows the percentage of movies for each category and movie set."}
fig4
```

The trend we have identified here is strong: movies that make the most
money are most often than not white-, male-, and Euro-centric. Even
looking beyond the dollar, we can see how scoring systems and awards are
biased towards this demographic as well. Although the American movie
industry continues achieved commercial success, it historically has, and
continues to, lack sufficient representation. While Hollywood has
undoubtedly created notable films like The Wizard of Oz, Gone With The
Wind, The Matrix, and Jurassic Park, the industry's focus on white males
has resulted in a significant loss of diverse perspectives and cinematic
experiences. It seems like when we are trying to judge a movie, we
should have a broader repertoire of measurements for how *good* it is
other than just money.

# Data Description

All of our datasets was scraped from public domains such as
[kaggle.com](https://kaggle.com/) and
[fivethirtyeight](https://fivethirtyeight.com/). In total, we used 4
datasets to support our research paper: <br>

1.  The Oscar Award, [1927 -
    2023](https://www.kaggle.com/datasets/unanimad/the-oscar-award):

-   10,765 Oscar nominations
-   scraped from the Official Academy Awards
-   7 variables: year, name, film, categories, win,... <br>

2.  Movie Industry: Four decades of movies,
    [1986-2016](https://www.kaggle.com/datasets/danielgrijalvas/movies):

-   6820 movies in the dataset (around 220 movies per year)
-   15 variables: budget, company, country, director, genre, name,....
    <br>

3.  All Time Worldwide Box Office,
    [1939-2021](https://www.kaggle.com/datasets/kkhandekar/all-time-worldwide-box-office)

-   contains the top movies based on the cumulative worldwide box office
-   7512 movies and 6 variables: rank, worldwide-international-domestic
    box office,... <br>

4.  Bechdel Test, 1970-2013 (from library(fivethirtyeight))

-   tests whether movies meet the following criteria: There are ≥ 2
    (named) female characters;these women talk to each othe; about
    something other than a man.
-   1794 movies, 15 variables: movie, result, grossings, ...

# Limitations

## Data

There are some limitations in the datasets. Firstmost, when comparing
the worldwide grossing amount of movies, we were unable to account for
inflation. The dataset "All Time Worldwide Box Office" scraped the the
amounts of international grossing from 1939 to 2021, but IMDb states
that ["all figures are not adjusted for
inflation"](https://help.imdb.com/article/contribution/titles/business-imdbpro-only/GEJUWSBB6WXH3RZ6#).
<br> According to a Minnesotan inflation calculator [1 U.S. Dollar in
1939 is worth \$19.48
today](https://www.minneapolisfed.org/about-us/monetary-policy/inflation-calculator),
which means that the amount of money occurring in different time periods
is not scaled to size. Additionally, in the dataset used for the racial
distribution of Oscars winners, the dataset only contained the racial
identities of best directors, actors, and actresses. This excludes 21
other award categories, which could have given more accurate insight
into the demographics of Oscars winners across the entire award
ceremony.\
<br> Furthermore, we used IMDb ratings to investigate how movies of
various grossing amounts are scored, but it is worth noting that the
website calculates an overall score from registered users casting their
votes. However, there has been a larger discussion around the
methodology of this system of movie-rating, with some people deeming
online movie voting systems to be ineffective. Additionally, it was
found that "most IMDb voters are male, which seems to skew the ranking
in favour of films that are aimed more towards men" [(Reynolds,
2017)](https://www.wired.co.uk/article/which-film-ranking-site-should-i-trust-rotten-tomatoes-imdb-metacritic).
It is worth acknowledging that IMDb ratings are a biased system of
ranking a film, however, this further aids our research question in
illustrating the complications that come with determining whether a
movie is "good". <br> Another limitation of this project is using The
Bechdel test as a measure of gender equality in film. The Bechdel test
is an infamous measure of Hollywood's gender imbalance, however it is an
oversimplified means of analyzing the role of women in film. It asks
three questions of a movie, and while astonishingly many films do not
pass that bar, the simplicity of this test "doesn't address the core
inequalities in Hollywood films" [(Hickey et al,
2017)](https://projects.fivethirtyeight.com/next-bechdel/). In the
dataset we used, there were many instances of "dubious" where the role
of women in the film were debated, and therefore, the pass/fail score
couldn't be determined. To create a more holistic analysis of gender
equality in Hollywood in the future, it is worth researching new tests
that include non-binary people, and expand the requirements. For ideas,
we can turn to "We pitted 50 movies against 12 new ways of measuring
Hollywood's gender imbalance" which suggests new tests that look beyond
white women, and the cast and crew of the film.

## Visualizations/ Overall Research

Our attempt throughout this research is to suggest different metrics to
compare and conclude a movie quality and public performance other than
its revenue and profit returns. Despite the various indicators we have
included to offer other avenues in determining a good movie, our "tests"
are simply not enough. With the limited scope of available and "perfect"
data, our research face real world limitations that fail to ascertain
the severity and array of Hollywood's inequalities that are beyond the
white male population. It also leaves out the population that stands
behind the camera in movie production such as screenwriters, producers,
set designers, etc. All of these are, hence, reflected in our
visualizations. However, we hope that our research can serve as an
incentive for the film industry as well as its audience to be more
critical of movies and movie making.

# Code Appendix

```{r, eval=FALSE, message=FALSE}
library(tidyverse)
library(splitstackshape)
library(dbplyr)
library(stringr)
library(readr)
library(ggplot2)
library(ggthemes)
library(fivethirtyeight)
library(highcharter)
library(scales)
library(rvest)
library(scales)
library(plotly)
library(gapminder)
library(forcats)
library(magrittr)


#Loading raw data
box_office <-read_csv("All Time Worldwide Box Office.csv")
movies_info <- read_csv("movies.csv")
oscars_award <- read_csv("the_oscar_award.csv")
bechdel <- data.frame(bechdel)
bechdelset <- read_csv("bechdelset.csv")
Bechdelmoney <- read_csv("Bechdelmoney.csv")
biopics <- data.frame(biopics)
RatingGross <- read_csv("RatingGross_edit2.csv")

```

```{r,eval=FALSE, message=FALSE}
#Data cleaning for figure 1
#average grossing for each top 20 scored

top_score <- movies_info %>% 
  select(name, score, year, gross) %>% 
  arrange(desc(score))

#average grossing for each top 20 scored

low_score <- movies_info %>% 
  select(name, score, year, gross) %>% 
  arrange(score)



oscarwins <-  movies_info %>% 
  filter(name %in% c("The Lord of the Rings: The Return of the King", "Titanic", "Ben-Hur", "West Side Story", "The English Patient", "The Last Emperor", "Gigi", "Slumdog Millionaire", "Amadeus", "Gandhi")) %>% 
 summarize(sum=sum(gross))

movies_info %>%
  group_by(year) %>%
  summarize(total_movies = n(),
            american_movies = sum(country == "United States"),
            percent_american = 100 * american_movies / total_movies)


doubledata <- movies_info %>%
  left_join(RatingGross,
    by = c("name", "year" = "Year"))


topgross <- doubledata %>% 
  filter(doubledata$Rank < 25) %>%  
  arrange(desc(`WorldwideBox Office`)) %>% 
  select(name, score.x, Rank, `WorldwideBox Office`)

duplicate_rows <- topgross[duplicated(topgross), ]
topgross <- unique(topgross)


toprate <- doubledata %>% 
  select(name, score.x, Rank, `WorldwideBox Office`) %>% 
  arrange(desc(score.x)) 

     
topgross_20 <- head(topgross, n = 20) %>% 
  select(name, score.x, `WorldwideBox Office`)
topscore_20 <- head(toprate, n = 20) %>% 
  select(name, score.x, `WorldwideBox Office`)



```

```{r,eval=FALSE, message=FALSE}
#Data cleaning for figure 2
# Changing Box Office variables into numerical values
box_office <-box_office %>% 
 mutate(`WorldwideBox Office`=as.numeric(str_replace_all(`WorldwideBox Office`,"[$,]",""))) %>% 
  mutate(`DomesticBox Office`=as.numeric(str_replace_all(`DomesticBox Office`,"[$,]",""))) %>%
  mutate(`InternationalBox Office`=as.numeric(str_replace_all(`InternationalBox Office`,"[$,]","")))

#Getting the Top 20 Box Office
box_office_top20 <- box_office %>%  
  arrange(Rank) %>% 
  head(20) %>% 
  mutate(Movie=ifelse(Movie=="Harry Potter and the Deathly Hallows:…", "Harry Potter and the Deathly Hallows: Part 2",Movie))


#Creating Oscar category data frame
oscars_category <- tibble(
levels(factor(oscars_award$category)))
  

oscars_category <- oscars_category %>% 
  rename("category"="levels(factor(oscars_award$category))") 
  

oscars_category <- oscars_category %>% 
  mutate(broad_category=word(category,1)) %>% 
  mutate(broad_category=
           case_when(broad_category =="ART" ~"ART DIRECTION",
                     broad_category == "BEST" ~ "BEST PICTURE",
                     broad_category == "FILM" ~ "FILM EDITING",
                     broad_category == "ACTOR" | broad_category=="ACTRESS" ~ "ACTING",
                    TRUE ~ broad_category)
            ) 

#Top 20 Box Office Movies and awards dataset by joining dataframes
box_office_top20_awards <- box_office_top20 %>% 
  inner_join(oscars_award,by=c("Movie"="film")) %>% 
  filter(Year == year_film) %>% 
  inner_join(oscars_category)  

box_office_top20_awards <- box_office_top20_awards %>% group_by(Movie,year_film) %>% 
  summarize(total=n()) %>%  inner_join(oscars_award,by=c("Movie"="film")) %>% 
  filter(year_film.x == year_film.y) %>% 
  inner_join(oscars_category)  %>% 
  select(Movie, year_film.x,total,year_ceremony,name,winner,broad_category)
```

```{r,eval=FALSE, message=FALSE}
#Data cleaning for figure 3
#Changing movie names so they match across movies_info and box_office_top20

movies_info <- movies_info %>%  mutate(name=case_when(
  name=="Star Wars: Episode VII - The Force Awakens" ~ "Star Wars Ep. VII: The Force Awakens",
  name =="Star Wars: Episode VIII - The Last Jedi" ~ "Star Wars Ep. VIII: The Last Jedi",
TRUE~name)) %>% 
  mutate(company=case_when(
    company=="Walt Disney Animation Studios" | company=="Walt Disney Pictures" ~"Walt Disney",
TRUE~company))

#Joinining movies_info and box_office_top20

box_office_top20_info<- box_office_top20 %>%
  inner_join(movies_info,by=c("Movie"="name","Year"="year"))

#Making top20 main character's race data frame
top20_race <- data.frame(star=box_office_top20_info$star,Race=c("White","White","White","White","White","White","Black","White","White","White","White","Black","White","White","White","White","White","White","White","White"))

#Joining box_office_top20_info with top20_race dataframe
box_office_top20_info <- box_office_top20_info %>% data.frame(top20_race) %>% select(!star.1)

```

```{r,eval=FALSE, message=FALSE}
#Data cleaning for figure 4

bechdelset <- bechdelset %>% 
  mutate(set_factor = factor(set)) 

bechdelsetav <- bechdelset %>% 
  group_by(set_factor, clean_test) %>% 
  summarize(count = n ())

bechdelsetav <- bechdelsetav %>% 
  mutate(percent = count/ 20 * 100)

bechdelav <- bechdel %>% 
  group_by(clean_test) %>%  
  summarize (count = n ())

bechdelav <- bechdelav %>%  
    mutate(percent = round(count/ 1794 * 100)) %>% 
    mutate(set_factor = "Average Bechdel Scores")

jointav <- rbind(bechdelsetav, bechdelav) 


jointav$clean_test <- factor(jointav$clean_test, levels = c("nowomen", "notalk", "men", "dubious", "ok"))

```

```{r,eval=FALSE, message=FALSE,fig.alt="A scatter plot showing the relationship between the IMDb score and worldwide box office gross for movies with different Bechdel test scores. Each point represents a movie and is colored based on its Bechdel test score. The legend shows the five Bechdel test scores: no women, no talk, men, dubious, and ok. The x-axis represents the IMDb score, and the y-axis represents the worldwide box office gross in millions/ billions of dollars. The tooltip displays the movie name, IMDb score, and worldwide grossing for each point."}
#Figure 1
colors <- c("#AC2528", "#E4792C", "#764484", "#346491", "#448746")

fig1<-plot_ly(bechdelset, x = ~score.x, y = ~`WorldwideBox Office`, color = ~clean_test, colors = colors, type = 'scatter', mode = 'markers',
  hoverinfo = 'text',
  text = ~paste('</br>', name, 
                '</br>', "IMDB Score:", score.x, 
                '</br>', "Worldwide Grossing:", comma(`WorldwideBox Office`))) %>% 
  layout(title = 'IMDB Score vs. Amount of Money Grossed', 
            xaxis = list(title = 'IMDB Score'), 
            yaxis = list(title = 'Worldwide Box Office'), 
           legend = list(title = list(text = "Bechdel Test Score"),
                       titles = list(topgross_20 = "Top 20 Grossing", topscore_20 = "Top 20 Scored")))




```

```{r,fig.width=10,fig.height=6,fig.alt="This bar graph shows the total number of oscar awards nominations of the top 20 movies with the highest Worldwide Box Office by Category and Wins",eval=FALSE, message=FALSE}
#Figure 2

fig2<-box_office_top20_awards %>% 
  ggplot(aes(x = fct_reorder(Movie, total,.fun=sum),alpha=winner,fill=fct_reorder(broad_category,winner))) + 
  geom_bar()+
  theme_classic() +
  theme(legend.position = "right")+
  scale_fill_viridis_d()+
  coord_flip()+
  labs(y="Total Nominations",x="Movie",title="Top 20 Movies with Highest Worldwide Box Office vs Oscars Awards",subtitle = "By Category and Wins",fill="Category",alpha="Winner")+
  theme(plot.title = element_text(face="bold",size=16),plot.subtitle = element_text(size=14),axis.title.x = element_text(size=14),axis.text.x = element_text(size=12),axis.title.y = element_text(size=14),axis.text.y = element_text(size=12))


```

```{r,fig.width=6,fig.height=4,fig.alt="This scatter plot displays the top 20 highest grossing movies of all time by their profit and the main character's race. It shows that out of 20 movies, 2 has a non-white main character.",eval=FALSE, message=FALSE}
#Figure 3
fig3<-box_office_top20_info %>% 
  mutate(Profit=gross-budget) %>%
  ggplot(aes(x=budget,y=gross,color=Race,size=Profit)) +
  geom_point()+
  theme_minimal()+
  scale_x_continuous(labels = label_comma())+
  scale_y_continuous(labels = label_comma())+
  scale_size_continuous(labels = label_comma())+
  scale_color_viridis_d(option="E")+
  labs(y="Total Gross",x="Budget",title="Top 20 Movies with Highest Worldwide Box Office",subtitle = "By Profit and Race of Main Character")+
  theme(plot.title = element_text(face="bold",size=12),plot.subtitle = element_text(size=10),axis.text.x = element_text(size=8))+
  annotate("text",x=200000000,y=1430000000,label="Black Panther",size=3,color="red3")+
   annotate("text",x=260000000,y=1750000000,label="The Lion King (2019)",size=3,color="red3")

  
```

```{r,eval=FALSE, message=FALSE,fig.alt="A stacked column chart showing the percentage distribution of movies that pass the Bechdel test by different movie sets. The x-axis represents the movie sets, and the y-axis represents the percentage of movies that pass the Bechdel test. The chart is divided into five categories based on the Bechdel test score: no women, no talk, men, dubious, and ok. The tooltip shows the percentage of movies for each category and movie set."}
#Figure 4


fig4<-hchart(jointav, "column", hcaes(x = set_factor, y = count, group = clean_test), stacking = "percent") %>% 
  hc_title(text = "Bechdel Test Scores") %>% 
  hc_colors(colors) %>% 
  hc_tooltip(pointFormat = "{series.name}: {point.percentage:.1f}%") %>% 
  hc_yAxis(title = "Percentage", labels = list(format = '{value}%')) %>%
  hc_xAxis(title = NULL) %>% 
  hc_colors(colors) %>% 
  hc_legend(enabled = TRUE)
```

# Other Sources

Brueggemann, Tom. "Theater Audiences Shrank by Half in the Last 4 Years.
Can Movies Get Them Back?" IMDb, 5 January 2023,
<https://www.imdb.com/news/ni63899408>. Accessed 3 May 2023. <br>
Hickey, Walt, et al. Creating The Next Bechdel Test \| FiveThirtyEight,
21 December 2017, <https://projects.fivethirtyeight.com/next-bechdel/>.
Accessed 3 May 2023. <br> "IMDb." Wikipedia,
<https://en.wikipedia.org/wiki/IMDb>. Accessed 3 May 2023. <br>
Reynolds, Matt. "You should ignore film ratings on IMDb and Rotten
Tomatoes." Wired UK, 24 October 2017,
<https://www.wired.co.uk/article/which-film-ranking-site-should-i-trust-rotten-tomatoes-imdb-metacritic>.
Accessed 3 May 2023. <br> Ugwu, Reggie. "The Hashtag That Changed the
Oscars: An Oral History (Published 2020)." The New York Times, 9
September 2020,
<https://www.nytimes.com/2020/02/06/movies/oscarssowhite-history.html>.
Accessed 3 May 2023. <br> Watkins, Albert. "Race and ethnicity in the
United States." Wikipedia,
<https://en.wikipedia.org/wiki/Race_and_ethnicity_in_the_United_States>.
Accessed 3 May 2023.
